Power simulations

### 2022-12-06 Power.Rmd
PowerRmd

```{r}
power_models$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                                      !is.na(arousal_c)&
                                        !is.na(BIO_CDA.PhasicMax)))

@@

summary(power_models$BIO_CDA.PhasicMax)
power_models$BIO_CDA.PhasicMax1<- power_models$BIO_CDA.PhasicMax
# 0.01571715 
fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"]
fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"] <- .1

@@

summary(power_models$BIO_CDA.PhasicMax1)
sim_SCR <- powerSim(power_models$pupil1, nsim = 100)

extendedscr100<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)

@@

extendedscr1002<- extend(power_models$BIO_CDA.PhasicMax, along="ssid", n=100)

pc_scr100_2<- powerCurve(extendedscr1002, along="ssid", nsim = 100)

plot(pc_scr100_2)
```

>>>>

```{r}
power_models$BIO_CDA.PhasicMax <- lmer(BIO_CDA.PhasicMax ~ valence_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                                      !is.na(arousal_c)&
                                        !is.na(BIO_CDA.PhasicMax)))

@@

summary(power_models$BIO_CDA.PhasicMax)
power_models$BIO_CDA.PhasicMax1<- power_models$BIO_CDA.PhasicMax
# 0.01571715 
fixef(power_models$BIO_CDA.PhasicMax)["valence_c"]

# reverse log to get proper unites wot meaninful effect size
0.01571715

ex

fixef(power_models$BIO_CDA.PhasicMax1)["valence_c"] <- -.1

@@

summary(power_models$BIO_CDA.PhasicMax1)
sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,test = fixed("arousal_c:valence_c", "z"),
                    nsim = 100)

# extendedscr100<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)
# extendedscr100_int<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)

@@

extendedscr1002<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)

# pc_scr100_2<- powerCurve(extendedscr1002, along="ssid", nsim = 100)

# extendedscr100_int@call
pc_scr100_int<- powerCurve(extendedscr1002,
                           test = fixed("arousal_c:valence_c", "z"),
                           along="ssid", nsim = 50)

plot(pc_scr100_int)
```
